\documentclass[a4paper, twoside]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage[noadjust]{cite}
\usepackage{csquotes}
\usepackage[english]{babel}
\usepackage{cite}
\usepackage{hyperref}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{array}
\usepackage{tikz}
\usepackage{etoolbox}
\usepackage{url}
\usepackage[linesnumbered]{algorithm2e}
\usepackage{enumitem}
\usepackage{pgfplots}
\pgfplotsset{compat=newest}

% make algorithm2e work with IEEEtran
\makeatletter
\newcommand{\removelatexerror}{\let\@latex@error\@gobble}
\makeatother

% adjust algorithm2e to IEEEtran style
\SetAlCapNameFnt{\footnotesize}
\SetAlCapFnt{\footnotesize}

% remove semicolons in algorithm env
\BeforeBeginEnvironment{algorithm}{\DontPrintSemicolon}

% group citations
\renewcommand{\citepunct}{,\penalty\citepunctpenalty\,}
\renewcommand{\citedash}{--}

% make urls work in biblatex
\def\UrlBreaks{\do\/\do-}
\apptocmd{\sloppy}{\hbadness 10000\relax}{}{}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

% cant fix underful hboxes with that many underscores in variable names
\hbadness=10000

\begin{document}

\title{Integrating Ecovisor into Mosaik Co-Simulation}
\markboth{Distributed and Operating Systems, TU Berlin, March 2023}{Steinke \&
Nickel: Integrating Ecovisor into Mosaik Co-Simulation}
\author{Marvin Steinke and Henrik Nickel\\\textit{Technische Universität Berlin}}

\maketitle

\begin{abstract}

    To reduce emissions, cloud platforms must increasingly rely on renewable
    energy sources such as solar and wind power. Nevertheless, the issue of
    volatility associated with these sources presents a significant challenge,
    since current energy systems conceal such unreliability in hardware. Souza
    et al. have devised a solution to this issue by creating an
    \enquote{ecovisor}. This system virtualizes the energy infrastructure and
    allows for software-defined control to be accessible by applications.
    Setting up the ecovisor to develop carbon-aware applications, however, can
    be costly and time consuming. To address this problem, we simulated the
    ecovisor and its virtual energy system and integrated in into a Mosaik
    co-simulation. With an API server and a Redis database we are enabling
    Software- (SIL) and Hardware-In-The-Loop (HIL) capabilities. To evaluate our
    approach, we created test cases using recorded solar and carbon data to
    demonstrate the accuracy of the ecovisor model's implementation and its
    ability to transfer data correctly between the model and the API server.

\end{abstract}

\section{Introduction}
\label{sec:introduction}
\input{sections/introduction}

\section{Background}
\label{sec:background}
\input{sections/background}

\section{Related Work}
\label{sec:related_work}
\input{sections/related_work}

\section{Approach}
\label{sec:approach}
\input{sections/approach}

\section{Evaluation}
\label{sec:evaluation}
\input{sections/evaluation}

\section{Future Work}
\label{sec:future_work}
\input{sections/future_work}

\section{Conclusion}
\label{sec:conclusion}
\input{sections/conclusion}

\bibliographystyle{IEEEtran}
\bibliography{refs}

\end{document}
